[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

head (same_sex) |>
  kable(
    col.names = c("Year","Total Marriages","Male", "Female", "All Civil", "Approved Civil", "All Religious"),
  booktabs = TRUE
  )
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustypeten
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Yellow), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 2010 and 2020 in England and Wales for Opposite-Sex Couples

ten_year <- subset(opposite_sex, year >= 2010 & year <= 2020)
ggplot(ten_year, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color="yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2010, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 60000, 5000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

## Same-Sex Couple Demographics
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-samesexdemographics
#| fig-pos: "H"
#| fig-cap: Annual Amount of Marriage Ceremonies Conducted Between 2014 and 2020 in England and Wales for Opposite-Sex Couples by Sex

@@

>>>>

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
head (same_sex) |>
  kable(
    col.names = c("Year","Total Marriages","Male", "Female", "All Civil", "Approved Civil", "All Religious"),
  booktabs = TRUE
  )
```

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustypeten
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Yellow), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 2011 and 2020 in England and Wales for Opposite-Sex Couples

ten_year <- subset(opposite_sex, year >= 2011 & year <= 2020)
ggplot(ten_year, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color = "yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2011, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 60000, 5000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-oppositedecades
#| tbl-cap: Total Amount of Marriage Ceremony Types Conducted by Decade (1971-2020)

ten_year1 <- subset(opposite_sex, year >= 1971 & year <= 1980)
ten_year2 <- subset(opposite_sex, year >= 1981 & year <= 1990)
ten_year3 <- subset(opposite_sex, year >= 1991 & year <= 2000)
ten_year4 <- subset(opposite_sex, year >= 2001 & year <= 2010)

opposite_decades <-
  data.frame(
  type = c("Civil", "Religious"),
  one = c(sum(ten_year1$all_civil), sum(ten_year1$all_religious)),
  two = c(sum(ten_year2$all_civil), sum(ten_year2$all_religious)),
  three = c(sum(ten_year3$all_civil), sum(ten_year3$all_religious)),
  four = c(sum(ten_year4$all_civil), sum(ten_year4$all_religious)),
  five = c(sum(ten_year$all_civil), sum(ten_year$all_religious)))

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
head (opposite_decades) |>
  kable(
    col.names = c("Ceremony Type","1971-1980","1981-1990", "1991-2000", "2001-2010", "2011-2020"),
  booktabs = TRUE
  )
```

## Same-Sex Couple Ceremony Totals
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-samesexdemographics
#| fig-pos: "H"
#| fig-cap: Annual Amount of Marriage Ceremonies Conducted Between 2014 and 2020 in England and Wales for Opposite-Sex Couples by Sex

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-samesextotals
#| tbl-cap: Total Amount of Same-Sex Marriage Ceremonies Conducted Between 2014 to 2020

same_sex_numbers <-
  data.frame(
    type = c("Civil", "Religious"),
    value = c(sum(same_sex$all_civil), sum(same_sex$all_religious))
  )

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd
head (same_sex_numbers) |>
  kable(
    col.names = c("Ceremony Type", "Total Number of Ceremonies Conducted"),
  booktabs = TRUE
  )

```
